Interview 4:\\
Interviewer : Sadath, Himanshu \\
Guest: Subject-4\\
\textbf{Transcript:}
\begin{enumerate}
    \item \emph{Interviewer:} Hi, Interviewee. I'd like to start by asking how often you use ferry/cruise services and for what purposes?\\
\emph{Interviewee:} I have used ferry services a couple of times since I have been here in Montreal. I have used it for sightseeing and to hang out with friends just to explore around. 
    \item \emph{Interviewer:} How much do you usually pay for a ticket for this ferry/cruise service and do you think the amount is justified?\\
\emph{Interviewee:} I have usually paid around \$8 for the ticket and I think the price is pretty justified for the amount of pleasure and peace it brings to me at such a great price.
    \item \emph{Interviewer:} What features do you think are necessary in a ticket vending machine for public transportation?\\
\emph{Interviewee:} Some of the features which I could think of are route information, variety of ticket options, contactless payment option like Apple Pay and real time updates of the transport schedule.
    \item \emph{Interviewer:} Some may argue that a ticket vending machine is not very important since it is a small machine that people may use only once a week or rarely for a few minutes. What do you think about this?\\
\emph{Interviewee:} Vending machines are a good alternative to the traditional standing in queue for purchasing a ticket system. As there is no human interaction required people can purchase a ticket within their own comfort with multiple choice of payment modes. Although it doesn't really solve a bigger problem in the system, it is good to have them on the side.
    \item \emph{Interviewer:} On a scale of 1 to 10, how important is it for the vending machine to be user-friendly and easy to navigate? \\
\emph{Interviewee:} I think the sole purpose of vending machines is to ease the overall process of getting the tickets without hassling too much by standing in long queues so on that scale it should be definitely 10.
    \item \emph{Interviewer:} In your opinion, would a touch screen interface or physical buttons be more effective for a ticket vending machine, and why?\\
\emph{Interviewee:} A touch screen interface might be more fascinating to look at, but a physical button interface does have its own advantages and one of the most important advantages is that it can easily be operated by someone who is visually impaired or blind.
    \item \emph{Interviewer:} Would you prefer a vending machine that only accepts cash or one that accepts both cash and card payments?\\
\emph{Interviewee:} Well the more choices, better it is. A lot of times you don't carry cash or I personally use my phone wallet to pay at different places so definitely I would prefer both cash and card payments.
    \item \emph{Interviewer:} What security measures do you think should be included in a ticket vending machine to prevent fraud or theft?\\
\emph{Interviewee:} Some of the security measures which I could think of are security cameras or maybe an anti theft alarm which will be triggered based on force sensors input.
    \item \emph{Interviewer:} Do you prefer a standalone vending machine or one that is integrated with other transportation services, such as bus or train systems?\\
\emph{Interviewee:} I would prefer a dynamic vending machine which can be used for multiple services. Although I think it can be difficult or confusing to operate, but if designed perfectly it can really solve the hassle of going to different machines to get things done.
    \item \emph{Interviewer:} How important is it for the vending machine to offer a variety of ticket options, such as single-use, day pass, or monthly pass?\\
\emph{Interviewee:} It is really important as it covers wider range of people. There might be some people who are tourists or they just want to try the service once so they don't have to pay the full amount of the ticket, on the other side if there is someone who travels many times a month, can get a discounted monthly pass and save some money through that.
    \item \emph{Interviewer:} What do you think about the option to purchase tickets online and pick them up at the vending machine, rather than purchasing them directly from the machine?\\
\emph{Interviewee:} I don't think it will make much of a difference as anyways you will have to go and pick up the ticket from the vending machine.
    \item \emph{Interviewer:} How important is it for the vending machine to have real-time schedule and route information?\\
\emph{Interviewee:} It is really important because as a customer I would like to know about all this information before I go in myself to make sure if we are not running late or the kind of route we are going for this time.
    \item \emph{Interviewer:} Would you prefer a vending machine that prints physical tickets or one that allows for mobile ticketing options?\\
\emph{Interviewee:} I would prefer the mobile ticketing option as carrying a physical ticket along with you is an extra hassle and it can be easily misplaced or lost.
    \item \emph{Interviewer:} Do you think the vending machine should be able to accept contactless payments, such as Apple Pay or Google Wallet?\\
\emph{Interviewee:} I think definitely yes. As I personally use Apple pay to pay for most of my purchases, feature like that is really convenient. 
    \item \emph{Interviewer:} Do you think it is important for the vending machine to have a feature for purchasing tickets for specific dates or times of travel?\\
\emph{Interviewee:}  A feature for purchasing ticket for a specific date or time can be a really good additional feature which can be helpful but I dont think it’s that important as it may increase the complexity of the system and lead to more confusion.
    \item \emph{Interviewer:} How important is it for the vending machine to have a clear and easy to understand pricing structure for tickets?\\
\emph{Interviewee:} It is really important as the confusion related to price can end up with more unsatisfied customers which leads to bad user experience overall and as no person is going to be physically present at the location, customers can’t even get a quick solution for their price related issues which they may encounter because of confusion.
    \item \emph{Interviewer:} How important is it for the vending machine to have a feature for live updates on service disruptions or delays?\\
\emph{Interviewee:} It is very important as the person should be able to know before purchasing the ticket that if there is any delay or disruption in the service so that they can decide to proceed further accordingly.    
    \item \emph{Interviewer:} Do you think it is important for the vending machine to have a feature that allows for contactless ticket pickup, such as through a QR code or NFC technology?\\
\emph{Interviewee:} I think features like these could have come really in handy at the time of COVID 19 as we can make use of technology to enhance the machine with features such as these but I don't think it is really that important for a vending machine to have features like these.
    \item \emph{Interviewer:} Would you prefer a vending machine that offers rewards or loyalty programs for frequent users?
?\\
\emph{Interviewee:} Most definitely. This will encourage users to use these services even more and I personally would love to have offers like these where I am getting something in reward along with my time of using the services.
    \item \emph{Interviewer:} How important is it for the vending machine to be equipped with a camera for security purposes?\\
\emph{Interviewee:} A security camera can come in real handy when it comes to theft prevention and protection. There it is quite important that vending machine is equipped with camera.
    \item \emph{Interviewer:} Do you think this specific ferry service needs a commuter card of some sort like the STM’s OPUS Card?\\
\emph{Interviewee:} That would be a really good idea as for frequent travellers or people who use the services quite often, that could save some bucks and make it easy to use these services, overall enhancing the user experience. 
    \item \emph{Interviewer:} Do you think it is important for the vending machine to have multilingual options for non-native speakers?\\
\emph{Interviewee:} I think the vending machine should most likely have a multilingual options because there are a lot of immigrants and foreign international travellers who would love to enjoy the services but may get restricted because of language barrier.
    \item \emph{Interviewer:} How important is it for the vending machine to be accessible for people with disabilities, such as those who use a wheelchair or have visual impairments?\\
\emph{Interviewee:} I don't think it is going to make much of a difference for the vending machine to be accessible for people with disabilities especially for those who are on wheelchairs or have visual impairments. Instead, a person on duty might be able to help them even more than they can help themselves with the vending machine.

{Interviewers:} Thank you for your time.
\end{enumerate}