Interview2:\\
Interviewer : Elvin, Kevin \\
Guest: Subject-2\\
\textbf{Transcript:}
\begin{enumerate}
    \item How important is it for a ticket vending machine to be able to accept multiple forms of payment, such as credit/debit cards, cash, and mobile payments?\\
Ans: For me,as far as I’m concerned, I like cashless payments, and, for that matter, contactless payment as well. So if there is Apple Pay, I would be very happy about it. 
    \item What features would you like to see in a ticket vending machine to make the ticket purchasing process more convenient?\\
Ans: Uhhh… A friendly user interface. English as the primary language. And, as I said, Cashless or contactless payment.
    \item What kind of security measures do you think should be implemented in a ticket vending machine to prevent fraud and theft?\\
Ans: Hmm.. I believe that someone has to come every day to ensure no one has installed a mask on the keypad, on the payment interface, that it records the payment details. It records strokes on a key.\\
Q: A key logger?\\
Ans: Yes, make sure there are no key loggers, especially in the payment interface-- the card payment.
    \item How important is it for a ticket vending machine to have a user-friendly interface for purchasing tickets?\\
Ans: I believe [it is] very important. The easier the better. Easier with fewer steps.
    \item Should a ticket vending machine offer the ability to print physical tickets, or should it only provide digital ticket options?\\
Ans: A bit of both, I prefer a digital ticket, but there are people who might want physical tickets for proof of travel, for business meetings.
    \item What types of tickets would you like to see offered in a ticket vending machine, such as single-use, day passes, or return trip tickets?\\
Ans: For a ferry, only single use, or day pass. Sorry, not day pass, I mean a return pass.
    \item Should a ticket vending machine offer the ability to purchase tickets for multiple people, such as a family or group of friends?\\
Ans: Yes, it’s more convenient as it will… it frees up lines.
    \item How important is it for a ticket vending machine to offer discounts or promotions for certain types of tickets or during certain times of the year?\\
Ans: Ya, it will be good to have discounts during vacation days, especially with some kind of recreational ticket.
    \item Should a ticket vending machine offer the option to purchase parking passes for those using the ferry/cruise service with a car?\\
Ans: In the ferry or outside the ferry station? You are asking for there to be a parking lot outside the ferry station. No, I think it complicates things.
    \item How important is it for a ticket vending machine to be available 24/7 for those who need to purchase tickets outside of normal business hours?\\
Ans: Aah, not important. I don’t think Ferry systems require pre-paid booking services.
    \item What kind of confirmation system should a ticket vending machine have to ensure that tickets are purchased successfully and accurately?\\
Ans: Uhh, once the quantity of tickets is… quantity of tickets are selected, just… Uhh… Confirm once the quantity and price, with tax.
    \item Should a ticket vending machine offer the ability to purchase tickets in advance, or only on the day of travel?\\
Ans: Only on the day of travel. For a ferry system, only on the day of travel.
    \item How important is it for a ticket vending machine to have a customer support system in case, uhhh… a u-- a user encounters issues while purchasing tickets?\\
Ans: Yes, it is important to have on-site assistance. On-site assistance would be better, rather than phone service, [because] you’ll have to call somebody.
    \item Should a ticket vending machine offer the ability to purchase tickets for multiple ferry/cruise routes or just one specific route?\\
Ans: Multiple routes.
    \item How important is it for a ticket vending machine to offer the ability to purchase tickets online or through a mobile app?\\
Ans: Actually, it’s a good feature to purchase online than through mobile.
    \item Should a ticket vending machine offer the ability to purchase tickets for multiple modes of transportation, such as buses or trains, in addition to ferries/cruise ships? The vending machines’ tickets, on top of boarding for ferries, should those also allow passage on other modes of transportations such as buses and trains?\\
Ans: Nah, no, nope. I would like the ferry system to be as simple as possible.
    \item Which type of payment confirmation options should a ticket vending machine offer, email or text message?\\
Ans: Text message.
    \item Should a ticket vending machine offer the ability to purchase tickets with a loyalty or rewards program?\\
Ans: Uhhh… Maybe, I don’t see how ferries… Maybe, maybe for a recreational ticket.
    \item How important is it for a ticket vending machine to have a clear and easy-to-understand pricing system for tickets?\\
Ans: I think it’s very important: the more simple it is the better.
    \item Should a ticket vending machine offer the ability to purchase tickets for both short- and long-distance ferry/cruise routes?\\
Ans: Yes.\\
Q: Would you like to expand on that?\\
Ans: Sure, okay sure. I think smaller routes need a different kind of interface, and the longer routes will need a different kind of [data?]..? Uhhh, but… The ability to purchase both [types of] tickets from the vending machine would be more convenient than to find the one vending machine that the uhh… to find the vending machine specific to your needs.
    \item How important is it for a ticket vending machine to offer the ability to purchase tickets for both one-way and round-trip travel?\\
Ans: I guess it’s important for me. It’s good. I-I-I, I will mostly take the ferry for roundtrip, so… I would like a round trip [ticket].
    \item Should a ticket vending machine offer the ability to purchase tickets in multiple languages for tourists and international travellers?\\
Ans: Yes, definitely. Especially in a famous city like Montreal, the ability to book in multiple languages would be good. Most, most importantly in English.
    \item How important is it for a ticket vending machine to offer the ability to purchase tickets for different seating classes or sections on the ferry/cruise ship?\\
Ans: For a long distance ferry, yes. For a short distance one, I think it would overcomplicate.
    \item Should a ticket vending machine offer the ability to purchase tickets with special accommodations for disabled or elderly passengers?\\
Ans: No. I believe the same tickets should be enough for both-- all kinds of passengers.
    \item How important is it for a ticket vending machine to have the ability to offer refunds or ticket cancellations in case of unexpected travel changes?\\
Ans: No, I don’t think refunds… Refunds are… I don’t think refunds are convenient in a vending machine. It should be done online or through customer service.
    \item Should a ticket vending machine offer the ability to purchase tickets for different age groups, such as children or seniors?\\
Ans: I think children under the age of 5 should get it for free, and uhh… Seniors over the age of… So are you asking me if it… about the tickets or the different price it should have..? Because it is a public transport, I believe that children under 5 and people over 65…\\
Q: What I mean is uhm… Uh, should they require to purchase… to make a purchase to board the ferry?\\
Ans: …No. The short distance ferry, no. But the long distance ferry should have a ticket, yes.
    \item How important is it for a ticket vending machine to have a clear and concise ticket selection process to prevent confusion for users?\\
Ans: It is extremely important. Very important. And uhh.. It determines if people will actually come back to the user interface and there will be problems-- if the user interface is not good, there will be more request in the customer care and uhh… The people who work behind the [inaudible, loud noise happened] will end up working more if the user interface is not good.
    \item Should a ticket vending machine offer the ability to purchase tickets for different time slots, such as morning or evening departures?\\
Ans: For the long distance, yes. For the short distance, no.
    \item Should a ticket vending machine offer the ability to purchase tickets with optional travel insurance?\\
Ans: Uhh, yes, it is good. Especially as it’s on water. It’s good to have insurance.\\
Q: How much would you pay for the extra insurance?\\
Ans: Short distance, maybe \$1. Long distance, \$5 to \$10… Not even \$10, maybe \$5 to \$7.
    \item How often do you use ferry/cruise services, and for what purposes?\\
Ans: I don’t use them often, but I have uhh, used ferries, ferries for [inaudible] and uhh.. It’s, it’s mostly for recreational purposes and not for like a [baby?] purpose. So I’m not sure I can… I’m not, I’m not the perfect person to talk about the [baby?] ferry, but the recreational one… Yeah.
    \item Uhh, how much would you pay for a ticket uhh, of[sic.] this ferry/cruise service? \\
Ans: Do you mean the short distance, or the long distance?\\
Q: Any ticket.\\
Ans: Short distance, maybe like \$4, \$5, \$4-\$5. Uhh, for the recreational one, mayyyyeah.. 20\$ or \$15. And for the long distance one from here to Toronto, probably, like, \$50, \$30, \$30 to \$50
    \item How do you usually purchase tickets for ferry/cruise services? Do you prefer buying tickets in advance or on the day of travel?\\
Ans: For the short distance one, on the day of travel. For the long distance one, maybe post-booking, but no request.\\
Q: Uhh, How do you usually purchase?\\
Ans: On the day of travel.
    \item What do you think about the option to purchase car tickets for the ferry/cruise service? Is it something you would use?\\
Ans: I don’t have a car now, but if I had a car, I would definitely.\\
Q: You would definitely?\\
Ans: Yes.
    \item How often do you travel with a car when using the ferry/cruise service? Is it something you typically find convenient?\\
Ans: I don’t have a car right now. I have only travelled on a ferry with a car like once, or twice maybe..? Not often.
    \item How do you typically plan your ferry/cruise trips? Do you find it easy to access the schedule and plan accordingly?\\
Ans: I have never faced a lot of difficulties, in that regard. But uhh, you should probably ask [inaudible, a different result?]…
    \item What do you think about the ticket vending machines located at, uhh, each stop? What would make them easy to use?\\
Ans: Yes, definitely. You should have a ticket vending machine at every stop. At every ferry pass.
    \item Have you ever used a recreational ticket for a ferry/cruise service before? Uhh, if so, what did you think about the experience?\\
Ans: Yes. It was very nice. Uhh.. When it’s recreational, it’s very fun. So I would prefer more emphasis on the recreational part of the experience than the daily commute.

Q: Thank you for your time.
\end{enumerate}