Interview3:\\
Interviewer : Himanshu, Swapnil \\
Guest: Subject-3\\
\textbf{Transcript:}
\begin{enumerate}
\item \emph{Interviewer:} Hello, I hope you are doing good, just wanna ask some question about our iGo vending machien. What do you think about the recreational ticket option, where the ferry makes a circle and starts and ends at the same station? Is it something you would be interested in?\\
\emph{Interviewee:} As a customer, I think the recreational ticket option sounds like a great idea. It would provide a unique way to experience the beauty of Montreal and its surroundings while enjoying a relaxing ferry ride. I would definitely be interested in this option, as it would allow me to explore the city from a different perspective and make for a fun outing with friends and family.
\item \emph{Interviewer:} What do you think about the option to scan a QR code for ticket entry, rather than manually entering an ID number?\\
\emph{Interviewee:} I think the option to scan a QR code for ticket entry is a great idea. It's much more convenient and efficient than manually entering an ID number, which can be time-consuming and prone to errors. With QR code scanning, the process is quick and seamless, making the overall ticket purchasing and entry experience much more pleasant.
\item \emph{Interviewer:} Have you ever experienced long lines or wait times when purchasing tickets or boarding the ferry/cruise ship?\\
\emph{Interviewee:} Yes, I have experienced long lines and wait times when purchasing tickets or boarding the ferry ship. It can be frustrating, but I understand that sometimes it's just part of the process. However, I appreciate any efforts made to streamline the ticket purchasing and boarding processes to minimize wait times and make the experience more enjoyable for passengers.
\item \emph{Interviewer:} What do you think about the overall design and layout of the ticket vending machines at the terminals?\\
\emph{Interviewee:}  I think the design and layout of the ticket vending machines should be simple and intuitive, with clear instructions and easy-to-use buttons. The interface should be visually appealing and easy to read, with prominent displays indicating prices, routes, and schedules. Additionally, the machines should be easily accessible and have clear signage to help customers locate them.
\item \emph{Interviewer:} How important is it for you to have access to a ferry/cruise service that offers both short- and long-distance travel options?\\
\emph{Interviewee:}  Uhh, it's very important for me to have access to a cruise service that offers both short- and long-distance travel options. This allows for more flexibility and convenience in travel planning, and it's great to have the option to explore different destinations without having to switch between different modes of transportation.
\item \emph{Interviewer:} Have you ever experienced any issues with the TVM schedule not being accurate or up-to-date?\\
\emph{Interviewee:}  Yes, I have experienced issues with the TVM schedule not being accurate or up-to-date in the past. It can be frustrating to rely on the schedule and find out that the information is incorrect, leading to missed or delayed travel plans. It would be great if the iGo vending machine software could ensure that the schedule is always up-to-date and reliable to avoid these issues.
\item \emph{Interviewer:}How important is it for you to have access to a ferry/cruise service that offers a variety of ticket options, rather than just one type of ticket?\\
\emph{Interviewee:} Umm, it's important for me to have access to a ferry/cruise service that offers a variety of ticket options. This allows me to choose the ticket that best suits my travel needs and budget. Having multiple ticket options can also help to make the ticket purchasing process more flexible and convenient.
\item \emph{Interviewer:}What do 
you think about the option to purchase a return trip ticket for two directions, rather than having to purchase two separate tickets?\\
\emph{Interviewee:}  I think it would be great if the iGo vending machine software offered the option to purchase a return trip ticket for two directions. It would save me time and effort by not having to purchase two separate tickets. Plus, it would provide a convenient and hassle-free experience for passengers, which is always appreciated when traveling.
\item \emph{Interviewer:}How do you typically find out about any changes or updates to the ferry/cruise service schedule or system?\\
\emph{Interviewee:}   I would appreciate receiving updates about changes to the ferry/cruise service schedule or system through multiple channels such as email, SMS, or push notifications on the iGo ticket vending machine. Having access to up-to-date information in real-time would greatly help me plan my travel and avoid any potential delays or inconveniences.
\item \emph{Interviewer:}What do you think about the customer service provided by the ferry/cruise service, such as staff friendliness and helpfulness?\\
\emph{Interviewee:}As a customer, I value friendly and helpful customer service from ferry/cruise staff. It's important for staff to be approachable and willing to assist passengers with any questions or concerns they may have. A positive customer service experience can greatly enhance the overall travel experience, making passengers more likely to use the service again in the future.
\item \emph{Interviewer:} How important is it for you to have access to a ferry/cruise service that operates year-round, rather than only during certain seasons?\\
\emph{Interviewee:} Umm, it's crucial for me to have access to a ferry/cruise service that operates year-round. I rely on this service for both business and personal travel, and having it available throughout the year provides me with greater flexibility and convenience. Additionally, it allows me to take advantage of travel opportunities whenever they arise, without having to worry about whether or not the ferry/cruise service is operating at that time.
\item \emph{Interviewer:} Have you ever experienced any issues with the ferry/cruise service being overcrowded or not having enough space for passengers and/or cars?\\
\emph{Interviewee:} Yes, I have experienced issues with overcrowding on ferry services. It can be uncomfortable when there isn't enough space for passengers and their belongings. It would be great if the iGo vending machine software could help alleviate these issues by streamlining the ticket purchasing process and ensuring that passengers have a smooth and stress-free travel experience.
\item \emph{Interviewer:} What do you think about the option to purchase a ticket that can be used for multiple trips, rather than just a single-use ticket?\\
\emph{Interviewee:}I think having the option to purchase a ticket that can be used for multiple trips is a great idea! It would save me time and effort since I wouldn't have to purchase a new ticket every time I travel. It would also be convenient for frequent travelers who use the ferry system regularly. Overall, I think it would be a very useful feature to have in the iGo vending machine software.
\item \emph{Interviewer:} How important is it for you to have access to a ferry/cruise service that offers Wi-Fi or other amenities while onboard?\\
\emph{Interviewee:}Um, well, I guess having access to Wi-Fi or other amenities on board a ferry or cruise would be pretty nice, but it's not necessarily a deal-breaker for me. It really depends on the length of the journey and what other options are available for entertainment or work. So, I would say it's moderately important, but not absolutely essential.
\item \emph{Interviewer:} Have you ever used the ferry/cruise service for commuting purposes, such as to get to work or school?\\
\emph{Interviewee:} Um, Yes, I have used ferry/cruise service for commuting purposes in the past. It was a decent experience, but sometimes the ticket purchasing process could be slow and inefficient. I hope that the iGo ticket vending machine software will make the process faster and more user-friendly.
\item \emph{Interviewer:} What do you think about the option to purchase a group ticket for 5, 7, or 8 seats in a car? Is it something you would use?\\
\emph{Interviewee:} Hmm, that's an interesting idea. I think the option to purchase a group ticket for 5, 7, or 8 seats in a car could be really useful for families or groups of friends traveling together. It would be convenient to be able to purchase all the tickets at once and ensure that everyone is seated together. Personally, I would definitely consider using this option if I were traveling with a group.
\item \emph{Interviewer:} How important is it for you to have access to a ferry/cruise service that offers accessibility accommodations, such as wheelchair ramps or audio announcements?\\
\emph{Interviewee:} Hmm, it's really important for me to have access to accessibility accommodations on a ferry or cruise service. Things like wheelchair ramps or audio announcements can make a huge difference in my ability to enjoy the experience and get around safely. So, I would say it's very important for me to have these types of accommodations available.
\item \emph{Interviewer:} Have you ever used the Ferry/Cruise Service system to travel to neighboring cities for recreational or tourist purposes?\\
\emph{Interviewee:} Um, no, I haven't actually used the Ferry/Cruise Service system before for any recreational or tourist purposes. But, I'm still interested in hearing more about how the iGo ticket vending machine software will work and how it will make the process of purchasing tickets more convenient and efficient.
\item \emph{Interviewer:} What do you think about the overall convenience and ease of use of the Ferry/ Cruise Service system?\\
\emph{Interviewee:} Hmm, well, I think the overall convenience and ease of use of the Ferry/Cruise Service system could be improved. Sometimes it can be a bit confusing to figure out how to purchase tickets, and the lines can be long and slow-moving. It would be great if there were more self-serve options, like vending machines, to make it quicker and easier to get tickets. And it would be nice if there were more clear signage and instructions to help passengers navigate the system.
\item \emph{Interviewer:} How important is it for you to have access to a ferry/cruise service that offers environmentally-friendly options, such as hybrid or electric ferries?\\
\emph{Interviewee:} Well, I think it's pretty important to have access to environmentally-friendly ferry/cruise options, like hybrid or electric ferries. I mean, we all need to do our part to help protect the planet, right? Plus, it's just nice to know that you're doing something good for the environment while you're traveling. So yeah, I'd say it's definitely something I would consider when choosing a ferry/cruise service.
\item  \emph{Interviewer:} Alright, so that will be all from my side. Thank you for your suggestions and interactive conversation.
\end{enumerate}