Interview 1\\
Interviewer : All members present. \\
Guest: Subject-1\\
\textbf{Transcript:}
\begin{enumerate}
    \item What features do you think are necessary in a ticket vending machine for public transportation?\\
Ans: For the vending machine itself, I’d like this machine to be easy to use, no queue for using it.
    \item So, How important is it for the vending machine to be user-friendly and easy to navigate on a scale of 1 to 10?\\
Ans: Umm, I'd say it's very important for the vending machine to be user friendly, as you won't be able to sell tickets faster.

Q: Okay That makes sense, But this is a very small , people will use this once a week or rarely for 5 mins , so do you think its as important?\\
Ans: We dont have a way to know that so its better 
    \item Do you think a touch screen interface or physical buttons would be more effective for a ticket vending machine an why?\\
	Ans: I personally like physical button, but I am aware touch interface becoming a fad recently\\
	Q: So, a touch interface will still be good for you right ?\\
Ans: I will be okay, but I would prefer physical buttons.
    \item Would you prefer a cash-only vending machine or one that accepts both cash and card payments?\\
Ans: Uhh, If it had to be one of the two, I would prefer card payments.

    \item What security measures do you think should be included in a ticket vending machine to prevent fraud or theft?\\
Ans: uhh, I think you are asking this to a wrong person.\\
	Q: Well what would you do ?\\
	Ans: Maybe have a security person standing next there. It might not be feasible but that's my answer. 
    \item How important is it for the vending machine to be accessible for people with disabilities, such as those who use a wheelchair or have visual impairments?\\
Ans: I mean ofc its important, it would be a good thing to get this machines accessible for people with disabilities.
    \item Would you prefer a standalone vending machine or one that is integrated with other transportation services, such as bus or train systems?\\
Ans: Umm, I mean, I am one to like it simple rather than integrated with other complex systems.
    \item Do you think it is important for the vending machine to have multilingual options for non-native speakers?\\
Ans: Yes, we are in Montreal, the two languages are English and French and considering other languages I don't have any particular preference but I wouldn’t favour that.
    \item How important is it for the vending machine to offer a variety of ticket options, such as single-use, day pass, or monthly pass?\\
Ans: Uh, I suppose it will be very convenient for people who like having the options. I would like to use single use tickets over the other choices.
    \item What do you think about the option to purchase tickets online and pick them up at the vending machine, rather than purchasing them directly from the machine?\\
Ans: Uhh personally, buying on site.
    \item How important is it for the vending machine to have real-time schedule and route information?\\
Ans: This is very convenient, I can know when I am late and can wait for the next ferry or vice versa in terms of hurry.
    \item Would you prefer a vending machine that prints physical tickets or one that allows for mobile ticketing options?\\
Ans: Uhh, I like the physical tickets rather than online.
    \item Do you think the vending machine should have a feature that allows for refunds or exchanges?\\
Ans: I would find that strange, I don't think this is a good idea.
    \item How important is it for the vending machine to be located in convenient areas, such as at major transportation hubs or in busy city centers?\\
Ans: I would think it has some advantages like compact, doesn’t take a lot of space. And the machines far from the ferry port will be inconvenient for me.
    \item Do you think it is important for the vending machine to have a customer service hotline for support?\\
Ans: I think it could be a good idea, but personally I have never used this kind of support .
    \item Would you prefer a vending machine that offers discounts or promotions for frequent users?\\
Ans: Umm, I mean you were already planning the monthly/day pass and that would be discount than normal price so it's fair.
    \item How important is it for the vending machine to be equipped with a camera for security purposes?\\
Ans: Uh, that’s a good question, security wise it’d be pretty good idea and for public location it's good.
    \item Do you think the vending machine should be able to accept contactless payments, such as Apple Pay or Google Wallet?\\
Ans: I personally, not in favour of contact less payment for security concerns.
    \item Would you prefer a vending machine that offers rewards or loyalty programs for frequent users?\\
Ans: Not personally, but I'm sure there are those in favor.
    \item How important is it for the vending machine to have a clear and visible display for ticket information and pricing?\\
Ans: Obviously very important.
    \item Do you think it is important for the vending machine to have a feature that allows for contactless ticket pickup, such as through a QR code or NFC technology?\\
Ans: Umm, I think physical ticket should be enough but if you could make it work than it could be good idea.
    \item Would you prefer a vending machine that offers a feature for pre-ordering tickets in advance of travel?\\
Ans: For me, advance ticket will be convenient.
    \item Do you think this specific Service(Ferry) needs a commuter card of some sort like Stm?\\
Ans: Right, if we dont use it often I suppose the ticketing system you have is fine.
    \item Do you think the vending machine should have a feature for scheduling or reserving seats on a ferry?\\
Ans: I dont reserving seats is a good idea, unless maybe it's like first class or economy class.
    \item How important is it for the vending machine to have a feature for live updates on service disruptions or delays?\\
Ans: Uhh, we have that similar ques before, i think that it would be good for providing updates which I can see on machine screen.
    \item How important is it for the vending machine to have a clear and easy-to-understand pricing structure for tickets?\\
Ans: uh,, I dont think its very important but the simplicity will make it easier to book tickets for me.
    \item Do you think it is important for the vending machine to have a feature for purchasing transit passes for a specific period of time, such as a month or a year?\\
Ans: yes, i dont use it often but people who uses very often will be good for them.
    \item How important is it for the vending machine to have a feature for purchasing?\\
Ans: For long distance, I’d say the comfort seats.
    \item Do you think it is important for the vending machine to have a feature for purchasing tickets for specific dates or times of travel?\\
Ans: Planning far ahead, but for people who wants to buy tickets in bulk that would be a good idea.
    \item Have you ever experienced any issues with the ferry/cruise service being overcrowded or not having enough space for passengers and/or cars?\\
Ans: Uhh before I used a ferry it was all good and enough space.
    \item How often do you use ferry/cruise services, and for what purposes?\\
Ans: I have used a ferry for a prom in high school.
    \item How much would you pay for a ticket for this ferry/cruise service?\\
Ans: Uh, I guess about \$5 would be fair price.
    \item What do you think about the option to purchase car tickets for the ferry/cruise service? Is it something you would use?\\
Ans: It is not the thing I would use but I am in favour our public transportation, but carrying a cars on ferry would be good idea.
    \item How often do you travel with a car when using the ferry/cruise service? Is it something you typically find convenient?\\
And: Ya, I don't use a car so not a good question for me.

\end{enumerate}